Variable creation ObjectInAction

### 2020-06-26 Final_Manuscript.Rmd
started MLM analyses

```{r packages}
library(papaja)
library(nlme)
library(haven)
library(devtools)
library(psych)
library(mosaic)
library(tidyr)
library(dplyr)
library(irr)
library(apaTables)
library(knitr)
library(kutils)
library(tidyverse)
library(lavaan)
library(xtable)
```

@@

 Rnew <- cbind(round(describe(x)[,3:4],2), Rnew)		     #describe x, M sD - put them in the matrix
 colnames(Rnew)[1:2] <- c("M","SD")					      		#Beschriftung der neuen Spalten
 Rnew <- Rnew[,1:(ncol(Rnew)-1)]							        	#delete the last column (ugly)

@@

#Smith--external and internal
smith_funcTSO_alpha <- psych::alpha(select(smith, tso_1, tso_2, tso_4, tso_7, tso_9), check.keys=TRUE)$total[2]
smith_physTSO_alpha <- psych::alpha(select(smith, tso_3, tso_5, tso_6, tso_8, tso_10), check.keys=TRUE)$total[2]

@@

## Analysis Strategy
This study sought to replicate the results of @garcia2016objectification’s study, done with male-female pairs, which used dyadic analysis to detect whether partners’ objectification of one another affected state self-objectification (SSO). See Figure\ \@ref(fig:2016figure) for the path analysis results of the previous study. We hope to investigate how the main effects found in the previous study relay to interactions between women: specifically, the relationship between state-other objectification and self-state objectification and the resulting effect of self-state objectification on inauthenticity during the interaction.

We used path analysis to obtain our estimates, but because our sample is nonindependent, we used the indistinguishable actor–partner interdependence model [@olsen2006structural]. The APIM can be defined as a "model of dyadic relationships that integrates a conceptual view of interdependence with the appropriate statistical techniques for measuring and testing it" [@olsen2006structural]. See Figure\ \@ref(fig:apim) for a basic APIM model. Unlike the original @garcia2016objectification study, our study deals with indistinguishable dyads, meaning the designation of who is designated as "actor" and who is designated as "partner" is arbitrary. Due to constraints of the basic APIM, in that this was an exploration of indistinguishable female dyads, we had to fix all path estimates to be the same across/between people and partners, in addition to all variances, covariances, endogenous intercepts, and exogenous means. Due to the complexity of the original @garcia2016objectification study, we also had to set the exogenous covariances equal. More specifically, the covariances between TSO, actor and partner objectification, and the interaction between actor TSO and partner objectification (and vice versa).

In order to interpret model fit, which refers to the ability of a model to reproduce the data (i.e., usually the varience-covariance matrix) we utilized both the I-SAT (saturated) model, and the Null model to ensure that all possible corresponding covariences are fixed to be equal across partners. We obtained fit estimates by subtracting the chi-square estimate for the I-SAT model from the analysis model [@olsen2006structural, @peugh2013analyzing].

```{r}
#Filtering for just one partnum and creating TSO * objectification interaction
dyad_cswomen <- clarksmith_women %>%
  mutate(TSO_P_SOO_A = TSO_P*a2pSOO_A,
         TSO_A_SOO_P = TSO_A*a2pSOO_P) %>%
  filter(partnum_A==1)

model <- '#####regressions 
howbody_avg_A ~ t*TSO_A + a*a2pSOO_A + b*a2pSOO_P + c*TSO_A_SOO_P
authenticity_A ~ d*howbody_avg_A
howbody_avg_P ~ t*TSO_P + a*a2pSOO_P + b*a2pSOO_A + c*TSO_P_SOO_A
authenticity_P ~ d*howbody_avg_P
trigram_score_A ~ e1*authenticity_A
careerasp_A ~ e2*authenticity_A
relag_A ~ e3*authenticity_A
trigram_score_P ~ e1*authenticity_P
careerasp_P ~ e2*authenticity_P
relag_P ~ e3*authenticity_P
######covariances
#endogenous
howbody_avg_A ~~ howbody_avg_P
authenticity_A ~~ authenticity_P
trigram_score_A ~~ trigram_score_P
careerasp_A ~~ careerasp_P
relag_A ~~ relag_P
trigram_score_A ~~ 0*careerasp_A
trigram_score_A ~~ 0*relag_A
trigram_score_A ~~ 0*careerasp_P
trigram_score_A ~~ 0*relag_P
careerasp_A ~~ 0*relag_A
careerasp_A ~~ 0*trigram_score_P
careerasp_A ~~ 0*relag_P
relag_A ~~ 0*trigram_score_P
relag_A ~~ 0*careerasp_P
trigram_score_P ~~ 0*careerasp_P
trigram_score_P ~~ 0*relag_P
careerasp_P ~~ 0*relag_P
#####variances
howbody_avg_A ~~ v1*howbody_avg_A
howbody_avg_P ~~ v1*howbody_avg_P
TSO_A ~~ v2*TSO_A
TSO_P ~~ v2*TSO_P
a2pSOO_A ~~ v3*a2pSOO_A
a2pSOO_P ~~ v3*a2pSOO_P
authenticity_A ~~ v4*authenticity_A
authenticity_P ~~ v4*authenticity_P
##endogenous intercepts
howbody_avg_A ~ i*1
howbody_avg_P ~ i*1
authenticity_A ~ i2*1
authenticity_P ~ i2*1
trigram_score_A ~ i3*1
trigram_score_P ~ i4*1
careerasp_A ~ i5*1
careerasp_P ~ i5*1
relag_A ~ i6*1
relag_P ~ i6*1
##exogenous means
TSO_A ~ m*1
TSO_P ~ m*1
a2pSOO_A ~ m2*1
a2pSOO_P ~ m2*1
TSO_P_SOO_A ~ m3*1
TSO_A_SOO_P ~ m3*1
## exogenous covariances
TSO_A_SOO_P ~~ c1*TSO_A
TSO_P_SOO_A ~~ c1*TSO_P
TSO_A_SOO_P ~~ c2*a2pSOO_P
TSO_P_SOO_A ~~ c2*a2pSOO_A
TSO_A ~~ c3*a2pSOO_P
TSO_P ~~ c3*a2pSOO_A
TSO_A ~~ c4*a2pSOO_A
TSO_P ~~ c4*a2pSOO_P
TSO_A_SOO_P ~~ c5*a2pSOO_A
TSO_P_SOO_A ~~ c5*a2pSOO_P
TSO_A_SOO_P ~~ c6*TSO_P
TSO_P_SOO_A ~~ c6*TSO_A
'

isatmodel <- '#####regressions 
#Part one/two
howbody_avg_A ~~ t*TSO_A
howbody_avg_A ~~ a*a2pSOO_A
howbody_avg_A ~~ b*a2pSOO_P 
howbody_avg_A ~~ c*TSO_A_SOO_P

howbody_avg_P ~~ t*TSO_P
howbody_avg_P ~~ a*a2pSOO_P 
howbody_avg_P ~~ b*a2pSOO_A 
howbody_avg_P ~~ c*TSO_P_SOO_A

TSO_A ~~ f*howbody_avg_P
TSO_P ~~ f*howbody_avg_A
TSO_A_SOO_P ~~ g*howbody_avg_P
TSO_P_SOO_A ~~ g*howbody_avg_A

#Part two/three
authenticity_A ~~ d*howbody_avg_A
authenticity_P ~~ d*howbody_avg_P
howbody_avg_A ~~ h*authenticity_P
howbody_avg_P ~~ h*authenticity_A

#Part three/four
trigram_score_A ~~ e1*authenticity_A
trigram_score_P ~~ e1*authenticity_P
careerasp_A ~~ e2*authenticity_A
careerasp_P ~~ e2*authenticity_P
relag_A ~~ e3*authenticity_A
relag_P ~~ e3*authenticity_P
trigram_score_A ~~ e4*relag_P
trigram_score_P ~~ e4*relag_A
trigram_score_A ~~ e5*careerasp_P
trigram_score_P ~~ e5*careerasp_A
trigram_score_A ~~ e6*trigram_score_P
#trigram_score_P ~~ e6*trigram_score_A
careerasp_A ~~ e7*relag_P
careerasp_P ~~ e7*relag_A
careerasp_A ~~ e8*careerasp_P
#careerasp_A ~~ e9*trigram_score_P
#careerasp_P ~~ e9*trigram_score_A
relag_A ~~ e10*relag_P

#One to three
#direct actor effects
authenticity_A ~~ k1*TSO_A_SOO_P
authenticity_P ~~ k1*TSO_P_SOO_A
authenticity_A ~~ k2*TSO_A
authenticity_P ~~ k2*TSO_P
authenticity_A ~~k3*a2pSOO_A
authenticity_P ~~k3*a2pSOO_P

#direct partner effects
authenticity_A ~~ k4*TSO_P_SOO_A
authenticity_P ~~k4*TSO_A_SOO_P
authenticity_A ~~ k5*TSO_P
authenticity_P ~~ k5*TSO_A
authenticity_A ~~ k6*a2pSOO_P
authenticity_P ~~ k6*a2pSOO_A

#One to four
#Direct actor effects
trigram_score_A ~~ l1*TSO_A_SOO_P
trigram_score_P ~~ l1*TSO_P_SOO_A
trigram_score_A ~~ l2*TSO_A
trigram_score_P ~~ l2*TSO_P
trigram_score_A ~~ l3*a2pSOO_A
trigram_score_P ~~ l3*a2pSOO_P
careerasp_A ~~ l4*TSO_A_SOO_P
careerasp_P ~~ l4*TSO_P_SOO_A
careerasp_A ~~ l5*TSO_A
careerasp_P ~~ l5*TSO_P
careerasp_A ~~ l6*a2pSOO_A
careerasp_P ~~ l6*a2pSOO_P
relag_A ~~ l7*TSO_A_SOO_P
relag_P ~~ l7*TSO_P_SOO_A
relag_A ~~ l8*TSO_A
relag_P ~~ l8*TSO_P
relag_A ~~ l9*a2pSOO_A
relag_P ~~ l9*a2pSOO_P

#direct partner effects
trigram_score_A ~~ m1*TSO_P_SOO_A
trigram_score_P ~~ m1*TSO_A_SOO_P
trigram_score_A ~~ m2*TSO_P
trigram_score_P ~~ m2*TSO_A
trigram_score_A ~~ m3*a2pSOO_P
trigram_score_P ~~ m3*a2pSOO_A
careerasp_A ~~ m4*TSO_P_SOO_A
careerasp_P ~~ m4*TSO_A_SOO_P
careerasp_A ~~ m5*TSO_P
careerasp_P ~~ m5*TSO_A
careerasp_A ~~ m6*a2pSOO_P
careerasp_P ~~ m6*a2pSOO_A
relag_A ~~ m7*TSO_P_SOO_A
relag_P ~~ m7*TSO_A_SOO_P
relag_A ~~ m8*TSO_P
relag_P ~~ m8*TSO_A
relag_A ~~ m9*a2pSOO_P
relag_P ~~ m9*a2pSOO_A

#Two to four
#direct actor effects
trigram_score_A ~~ o1*howbody_avg_A
trigram_score_P ~~ o1*howbody_avg_P
careerasp_A ~~ o2*howbody_avg_A
careerasp_P ~~ o2*howbody_avg_P
relag_A ~~ o3*howbody_avg_A
relag_P ~~ o3*howbody_avg_P

#direct partner effects
trigram_score_A ~~ o1*howbody_avg_P
trigram_score_P ~~ o1*howbody_avg_A
careerasp_A ~~ o2*howbody_avg_P
careerasp_P ~~ o2*howbody_avg_A
relag_A ~~ o3*howbody_avg_P
relag_P ~~ o3*howbody_avg_A

######covariances
#endogenous
howbody_avg_A ~~ howbody_avg_P
authenticity_A ~~ authenticity_P
#trigram_score_A ~~ trigram_score_P
#careerasp_A ~~ careerasp_P
#relag_A ~~ relag_P
trigram_score_A ~~ q1*careerasp_A 
trigram_score_A ~~ q2*relag_A

careerasp_A ~~ q3*relag_A

trigram_score_P ~~ q1*careerasp_P
trigram_score_P ~~ q2*relag_P

careerasp_P ~~ q3*relag_P

trigram_score_A ~~ q4*careerasp_P
trigram_score_A ~~ q5*relag_P

trigram_score_P ~~ q4*careerasp_A
trigram_score_P ~~ q5*relag_A

careerasp_A ~~ q6*relag_P
careerasp_P ~~ q6*relag_A

#####variances
howbody_avg_A ~~ v1*howbody_avg_A
howbody_avg_P ~~ v1*howbody_avg_P
TSO_A ~~ v2*TSO_A
TSO_P ~~ v2*TSO_P
a2pSOO_A ~~ v3*a2pSOO_A
a2pSOO_P ~~ v3*a2pSOO_P
authenticity_A ~~ v4*authenticity_A
authenticity_P ~~ v4*authenticity_P
##endogenous intercepts
howbody_avg_A ~ i*1
howbody_avg_P ~ i*1
authenticity_A ~ i2*1
authenticity_P ~ i2*1
trigram_score_A ~ i3*1
trigram_score_P ~ i4*1
careerasp_A ~ i5*1
careerasp_P ~ i5*1
relag_A ~ i6*1
relag_P ~ i6*1
##exogenous means
TSO_A ~ m*1
TSO_P ~ m*1
a2pSOO_A ~ m2*1
a2pSOO_P ~ m2*1
TSO_P_SOO_A ~ m3*1
TSO_A_SOO_P ~ m3*1
## exogenous covariances
TSO_A_SOO_P ~~ c1*TSO_A
TSO_P_SOO_A ~~ c1*TSO_P
TSO_A_SOO_P ~~ c2*a2pSOO_P
TSO_P_SOO_A ~~ c2*a2pSOO_A
TSO_A ~~ c3*a2pSOO_P
TSO_P ~~ c3*a2pSOO_A
TSO_A ~~ c4*a2pSOO_A
TSO_P ~~ c4*a2pSOO_P
TSO_A_SOO_P ~~ c5*a2pSOO_A
TSO_P_SOO_A ~~ c5*a2pSOO_P
TSO_A_SOO_P ~~ c6*TSO_P
TSO_P_SOO_A ~~ c6*TSO_A
'

fit <- sem(model, data=dyad_cswomen)
```

```{r sem, include=TRUE, results='asis'}
fit_table <- xtable(parameterEstimates(fit))

fit_table <- fit_table %>%
  filter(op=="~") %>%
  mutate(lhs = ifelse(lhs == "howbody_avg_A", "Actor SSO", 
                      ifelse(lhs=="authenticity_A", "Actor Authenticity",
                             ifelse(lhs=="howbody_avg_P", "Partner SSO",
                                    ifelse(lhs=="authenticity_P", "Partner Authenticity", 
                                           ifelse(lhs=="relag_A", "Actor Rel. Agency",
                                                  ifelse(lhs=="relag_P", "Partner Rel. Agency",
                                                         ifelse(lhs=="careerasp_A", "Actor Career Aspirations",
                                                                ifelse(lhs=="careerasp_P", "Partner Career Aspirations",
                                                                       ifelse(lhs=="trigram_score_A", "Actor Cog. Performance",
                                                                              ifelse(lhs=="trigram_score_P", "Partner Cog. Performance", NA)))))))))),
         rhs = ifelse(rhs=="TSO_A", "Actor TSO",
                      ifelse(rhs=="a2pSOO_A", "Actor Obj. of Partner",
                             ifelse(rhs=="a2pSOO_P", "Partner Obj. of Actor",
                                    ifelse(rhs=="TSO_A_SOO_P", "Actor TSO x Partner Obj.",
                                           ifelse(rhs == "howbody_avg_A", "Actor SSO",
                                                  ifelse(rhs=="howbody_avg_P", "Partner SSO",
                                                         ifelse(rhs=="TSO_P", "Partner TSO",
                                                                ifelse(rhs=="TSO_P_SOO_A", "Partner TSO x Actor Obj.",
                                                                       ifelse(rhs=="authenticity_A", "Actor Authenticity", 
                                                                              ifelse(rhs=="authenticity_P", "Partner Authenticity", NA))))))))))) %>%
  select(lhs, op, rhs, est, se, z, pvalue) %>%
  #taking out partner-partner estimates
  slice(1:5,11:13)

colnames(fit_table) <- c("Path", "", "", "Estimate", "SE", "z-value", "p-value")

apa_table(fit_table, caption = "Estimates from final Path Analysis Model", font_size = "small")
```

```{r semfigure, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Path Analysis Model with Estimates"}
include_graphics("SEMfigure.png")
```

##Main Results
All model estimates and p-values are found in Table\ \@ref(tab:sem) and the relationships are depicted in Figure\ \@ref(fig:semfigure). The most important findings from @garcia2016objectification were the significant partner effect between actor SSO and partner objectification (specifically men's objectification of women and women's SSO), and the link between actor SSO and actor authenticity (also specifically for women). We did not find a significant effect between actor SSO and actor authenticity ($\beta$= -.10, $p$=.38), which means we do not have evidence to support the idea that partner objectification is the cause for the negative effects related to relationship inauthenticity. However, we did find a significant relationship between partner objectification and actor SSO ($\beta$= .25, $p$=.03), which supports our hypothesis that objectification from other women also causes women to self-objectify just as it does in interactions between male-female pairs. We also found a significantly negative effect of authenticity on career aspirations ($\beta$= .18, $p$=.01) and relationship agency ($\beta$=.27, $p$=.01). We found that the model had good fit ($\chi^2$=22.33, $df$=34). In this case, a good fit indicates that there are no direct effects of SSO or SOO on the outcomes on cognitive performance, relationship agency, and career aspirations, which indicates that the path we chose makes sense.

>>>>

```{r packages, warning = FALSE, message = FALSE}
library(papaja)
library(nlme)
library(haven)
library(devtools)
library(psych)
library(mosaic)
library(tidyr)
library(dplyr)
library(irr)
library(apaTables)
library(knitr)
library(kutils)
library(tidyverse)
library(lavaan)
library(xtable)
```

@@

 Rnew <- cbind(round(describe(x)[,3:4],2), Rnew)		 #describe x, M sD - put them in the matrix
 colnames(Rnew)[1:2] <- c("M","SD")			#Beschriftung der neuen Spalten-"labeling of the new columns"
 Rnew <- Rnew[,1:(ncol(Rnew)-1)]							   	#delete the last column (ugly)

@@

#Smith--external and internal
smith_funcTSO_alpha <- psych::alpha(select(smith, tso_1, tso_2, tso_4, tso_7, tso_9), check.keys=TRUE)$total[2]
smith_physTSO_alpha <- psych::alpha(select(smith, tso_3, tso_5, tso_6, tso_8, tso_10), check.keys=TRUE)$total[2]
```

@@

## Analysis Strategy
This study sought to replicate the results of @garcia2016objectification’s study, done with male-female pairs, which used a dyadic path analysis to detect whether partners’ objectification of one another affected state self-objectification (SSO). See Figure\ \@ref(fig:2016figure) for the results of the analysis from this previous study. We hope to investigate how the central effects found in the previous study relate to interactions between two women. Specifically, we are interested in testing the relationship between state-other objectification and SSO, and how SSO in turn, affecs feelings of inauthenticity during the interaction. In addition, we will also test if the effect of other-objectification in an interaction on SSO is only present for those women who are high in trait self-objectification, as in @garcia2016objectification. Further, we will investigate the realtionships between experiencing interaction inauthenticity and relationship agency, career aspirations, and cognitive performance.

While @garcia2016objectification used dyadic path analysis, we will conduct our dyadic analyses using multilevel modeling. Dyadic analyses for distingishable dyads (e.g., mixed-gender interacting pairs) is more natural in Structual Equation Modeling (SEM) than it is for indistinguishable dayds (e.g., same-gender interacting pairs) [@ledermann2017analyzing; @garcia2015moderation]. One reason for this asymmetry is that, due to the arbitrary distinctions made bewteen "partner 1" and "partner 2" in indistinguishable dyads, many estimates need to be fixed to be equal (i.e., paths, variances, covariances, endogenous intercepts, and exogenous means) for indistinguishable dyads but these equality contraints should not then be considered in the degrees of freedom calculations for fit estimations [@olsen2006structural]. Further, @olsen2006structural detail how a new independence model and the corresponding fit measure should be re-calculated for indistinguishable dyads models. The current study uses dyadic multilevel modeling (MLM) to test all relationships and mediation paterns. See @ledermann2017analyzing for a more complete discussion of the considerations for using SEM versus MLM for dyadic analysis.

Testing the @garcia2016objectification model on the current, same-gender, sample, involves using the Actor-Partner Independence Model (APIM) approch for each outcome variable (i.e., endogenous variable in Figure\ \@ref(fig:2016figure)). Thus, we ran five APIM's to test all the hypothesized relationships. See Figure\ \@ref(fig:apim) for a basic APIM model. The APIM includes effects due to one's own, as well as one's partner's, predictor variables ($X$'s) on the one's own outcome variable ($Y$). Unlike the original @garcia2016objectification study, our study deals with indistinguishable dyads, meaning the designation of who is designated as "actor" and who is designated as "partner" is arbitrary. Recall that the indistinguiahble nature of the dyads in the current study led us to choose the MLM approach over SEM. These analyses are considered exploratory, given the lack of prior research theorizing about these linkages.

<!-- The model differences as a result of adopting this MLM approach include an examination of the partner effect of TSO on SSO, partner effect of SSO on authenticity, and partner effects of authenticity on congitive performance, relationship agency, and career aspirations.  -->

<!-- We used path analysis to obtain our estimates, but because our sample is nonindependent, we used the indistinguishable actor–partner interdependence model [@olsen2006structural]. The APIM can be defined as a "model of dyadic relationships that integrates a conceptual view of interdependence with the appropriate statistical techniques for measuring and testing it" [@olsen2006structural]. Due to the complexity of the original @garcia2016objectification study, we also had to set the exogenous covariances equal. More specifically, the covariances between TSO, actor and partner objectification, and the interaction between actor TSO and partner objectification (and vice versa). -->

<!-- In order to interpret model fit, which refers to the ability of a model to reproduce the data (i.e., usually the varience-covariance matrix) we utilized both the I-SAT (saturated) model, and the Null model to ensure that all possible corresponding covariences are fixed to be equal across partners. We obtained fit estimates by subtracting the chi-square estimate for the I-SAT model from the analysis model [@olsen2006structural, @peugh2013analyzing]. -->

```{r}
# #Filtering for just one partnum and creating TSO * objectification interaction
# dyad_cswomen <- clarksmith_women %>%
#   mutate(TSO_P_SOO_A = TSO_P*a2pSOO_A,
#          TSO_A_SOO_P = TSO_A*a2pSOO_P) %>%
#   filter(partnum_A==1)
# 
# 
# model <- '#####regressions 
# howbody_avg_A ~ t*TSO_A + a*a2pSOO_A + b*a2pSOO_P + c*TSO_A_SOO_P
# authenticity_A ~ d*howbody_avg_A
# howbody_avg_P ~ t*TSO_P + a*a2pSOO_P + b*a2pSOO_A + c*TSO_P_SOO_A
# authenticity_P ~ d*howbody_avg_P
# trigram_score_A ~ e1*authenticity_A
# careerasp_A ~ e2*authenticity_A
# relag_A ~ e3*authenticity_A
# trigram_score_P ~ e1*authenticity_P
# careerasp_P ~ e2*authenticity_P
# relag_P ~ e3*authenticity_P
# ######covariances
# #endogenous
# howbody_avg_A ~~ howbody_avg_P
# authenticity_A ~~ authenticity_P
# trigram_score_A ~~ trigram_score_P
# careerasp_A ~~ careerasp_P
# relag_A ~~ relag_P
# trigram_score_A ~~ 0*careerasp_A
# trigram_score_A ~~ 0*relag_A
# trigram_score_A ~~ 0*careerasp_P
# trigram_score_A ~~ 0*relag_P
# careerasp_A ~~ 0*relag_A
# careerasp_A ~~ 0*trigram_score_P
# careerasp_A ~~ 0*relag_P
# relag_A ~~ 0*trigram_score_P
# relag_A ~~ 0*careerasp_P
# trigram_score_P ~~ 0*careerasp_P
# trigram_score_P ~~ 0*relag_P
# careerasp_P ~~ 0*relag_P
# #####variances
# howbody_avg_A ~~ v1*howbody_avg_A
# howbody_avg_P ~~ v1*howbody_avg_P
# TSO_A ~~ v2*TSO_A
# TSO_P ~~ v2*TSO_P
# a2pSOO_A ~~ v3*a2pSOO_A
# a2pSOO_P ~~ v3*a2pSOO_P
# authenticity_A ~~ v4*authenticity_A
# authenticity_P ~~ v4*authenticity_P
# ##endogenous intercepts
# howbody_avg_A ~ i*1
# howbody_avg_P ~ i*1
# authenticity_A ~ i2*1
# authenticity_P ~ i2*1
# trigram_score_A ~ i3*1
# trigram_score_P ~ i4*1
# careerasp_A ~ i5*1
# careerasp_P ~ i5*1
# relag_A ~ i6*1
# relag_P ~ i6*1
# ##exogenous means
# TSO_A ~ m*1
# TSO_P ~ m*1
# a2pSOO_A ~ m2*1
# a2pSOO_P ~ m2*1
# TSO_P_SOO_A ~ m3*1
# TSO_A_SOO_P ~ m3*1
# ## exogenous covariances
# TSO_A_SOO_P ~~ c1*TSO_A
# TSO_P_SOO_A ~~ c1*TSO_P
# TSO_A_SOO_P ~~ c2*a2pSOO_P
# TSO_P_SOO_A ~~ c2*a2pSOO_A
# TSO_A ~~ c3*a2pSOO_P
# TSO_P ~~ c3*a2pSOO_A
# TSO_A ~~ c4*a2pSOO_A
# TSO_P ~~ c4*a2pSOO_P
# TSO_A_SOO_P ~~ c5*a2pSOO_A
# TSO_P_SOO_A ~~ c5*a2pSOO_P
# TSO_A_SOO_P ~~ c6*TSO_P
# TSO_P_SOO_A ~~ c6*TSO_A
# '
# 
# isatmodel <- '#####regressions 
# #Part one/two
# howbody_avg_A ~~ t*TSO_A
# howbody_avg_A ~~ a*a2pSOO_A
# howbody_avg_A ~~ b*a2pSOO_P 
# howbody_avg_A ~~ c*TSO_A_SOO_P
# 
# howbody_avg_P ~~ t*TSO_P
# howbody_avg_P ~~ a*a2pSOO_P 
# howbody_avg_P ~~ b*a2pSOO_A 
# howbody_avg_P ~~ c*TSO_P_SOO_A
# 
# TSO_A ~~ f*howbody_avg_P
# TSO_P ~~ f*howbody_avg_A
# TSO_A_SOO_P ~~ g*howbody_avg_P
# TSO_P_SOO_A ~~ g*howbody_avg_A
# 
# #Part two/three
# authenticity_A ~~ d*howbody_avg_A
# authenticity_P ~~ d*howbody_avg_P
# howbody_avg_A ~~ h*authenticity_P
# howbody_avg_P ~~ h*authenticity_A
# 
# 
# #Part three/four
# trigram_score_A ~~ e1*authenticity_A
# trigram_score_P ~~ e1*authenticity_P
# careerasp_A ~~ e2*authenticity_A
# careerasp_P ~~ e2*authenticity_P
# relag_A ~~ e3*authenticity_A
# relag_P ~~ e3*authenticity_P
# trigram_score_A ~~ e4*relag_P
# trigram_score_P ~~ e4*relag_A
# trigram_score_A ~~ e5*careerasp_P
# trigram_score_P ~~ e5*careerasp_A
# trigram_score_A ~~ e6*trigram_score_P
# #trigram_score_P ~~ e6*trigram_score_A
# careerasp_A ~~ e7*relag_P
# careerasp_P ~~ e7*relag_A
# careerasp_A ~~ e8*careerasp_P
# #careerasp_A ~~ e9*trigram_score_P
# #careerasp_P ~~ e9*trigram_score_A
# relag_A ~~ e10*relag_P
# 
# #One to three
# #direct actor effects
# authenticity_A ~~ k1*TSO_A_SOO_P
# authenticity_P ~~ k1*TSO_P_SOO_A
# authenticity_A ~~ k2*TSO_A
# authenticity_P ~~ k2*TSO_P
# authenticity_A ~~k3*a2pSOO_A
# authenticity_P ~~k3*a2pSOO_P
# 
# #direct partner effects
# authenticity_A ~~ k4*TSO_P_SOO_A
# authenticity_P ~~k4*TSO_A_SOO_P
# authenticity_A ~~ k5*TSO_P
# authenticity_P ~~ k5*TSO_A
# authenticity_A ~~ k6*a2pSOO_P
# authenticity_P ~~ k6*a2pSOO_A
# 
# #One to four
# #Direct actor effects
# trigram_score_A ~~ l1*TSO_A_SOO_P
# trigram_score_P ~~ l1*TSO_P_SOO_A
# trigram_score_A ~~ l2*TSO_A
# trigram_score_P ~~ l2*TSO_P
# trigram_score_A ~~ l3*a2pSOO_A
# trigram_score_P ~~ l3*a2pSOO_P
# careerasp_A ~~ l4*TSO_A_SOO_P
# careerasp_P ~~ l4*TSO_P_SOO_A
# careerasp_A ~~ l5*TSO_A
# careerasp_P ~~ l5*TSO_P
# careerasp_A ~~ l6*a2pSOO_A
# careerasp_P ~~ l6*a2pSOO_P
# relag_A ~~ l7*TSO_A_SOO_P
# relag_P ~~ l7*TSO_P_SOO_A
# relag_A ~~ l8*TSO_A
# relag_P ~~ l8*TSO_P
# relag_A ~~ l9*a2pSOO_A
# relag_P ~~ l9*a2pSOO_P
# 
# #direct partner effects
# trigram_score_A ~~ m1*TSO_P_SOO_A
# trigram_score_P ~~ m1*TSO_A_SOO_P
# trigram_score_A ~~ m2*TSO_P
# trigram_score_P ~~ m2*TSO_A
# trigram_score_A ~~ m3*a2pSOO_P
# trigram_score_P ~~ m3*a2pSOO_A
# careerasp_A ~~ m4*TSO_P_SOO_A
# careerasp_P ~~ m4*TSO_A_SOO_P
# careerasp_A ~~ m5*TSO_P
# careerasp_P ~~ m5*TSO_A
# careerasp_A ~~ m6*a2pSOO_P
# careerasp_P ~~ m6*a2pSOO_A
# relag_A ~~ m7*TSO_P_SOO_A
# relag_P ~~ m7*TSO_A_SOO_P
# relag_A ~~ m8*TSO_P
# relag_P ~~ m8*TSO_A
# relag_A ~~ m9*a2pSOO_P
# relag_P ~~ m9*a2pSOO_A
# 
# #Two to four
# #direct actor effects
# trigram_score_A ~~ o1*howbody_avg_A
# trigram_score_P ~~ o1*howbody_avg_P
# careerasp_A ~~ o2*howbody_avg_A
# careerasp_P ~~ o2*howbody_avg_P
# relag_A ~~ o3*howbody_avg_A
# relag_P ~~ o3*howbody_avg_P
# 
# #direct partner effects
# trigram_score_A ~~ o1*howbody_avg_P
# trigram_score_P ~~ o1*howbody_avg_A
# careerasp_A ~~ o2*howbody_avg_P
# careerasp_P ~~ o2*howbody_avg_A
# relag_A ~~ o3*howbody_avg_P
# relag_P ~~ o3*howbody_avg_A
# 
# 
# ######covariances
# #endogenous
# howbody_avg_A ~~ howbody_avg_P
# authenticity_A ~~ authenticity_P
# #trigram_score_A ~~ trigram_score_P
# #careerasp_A ~~ careerasp_P
# #relag_A ~~ relag_P
# trigram_score_A ~~ q1*careerasp_A 
# trigram_score_A ~~ q2*relag_A
# 
# careerasp_A ~~ q3*relag_A
# 
# trigram_score_P ~~ q1*careerasp_P
# trigram_score_P ~~ q2*relag_P
# 
# careerasp_P ~~ q3*relag_P
# 
# trigram_score_A ~~ q4*careerasp_P
# trigram_score_A ~~ q5*relag_P
# 
# 
# trigram_score_P ~~ q4*careerasp_A
# trigram_score_P ~~ q5*relag_A
# 
# careerasp_A ~~ q6*relag_P
# careerasp_P ~~ q6*relag_A
# 
# 
# #####variances
# howbody_avg_A ~~ v1*howbody_avg_A
# howbody_avg_P ~~ v1*howbody_avg_P
# TSO_A ~~ v2*TSO_A
# TSO_P ~~ v2*TSO_P
# a2pSOO_A ~~ v3*a2pSOO_A
# a2pSOO_P ~~ v3*a2pSOO_P
# authenticity_A ~~ v4*authenticity_A
# authenticity_P ~~ v4*authenticity_P
# ##endogenous intercepts
# howbody_avg_A ~ i*1
# howbody_avg_P ~ i*1
# authenticity_A ~ i2*1
# authenticity_P ~ i2*1
# trigram_score_A ~ i3*1
# trigram_score_P ~ i4*1
# careerasp_A ~ i5*1
# careerasp_P ~ i5*1
# relag_A ~ i6*1
# relag_P ~ i6*1
# ##exogenous means
# TSO_A ~ m*1
# TSO_P ~ m*1
# a2pSOO_A ~ m2*1
# a2pSOO_P ~ m2*1
# TSO_P_SOO_A ~ m3*1
# TSO_A_SOO_P ~ m3*1
# ## exogenous covariances
# TSO_A_SOO_P ~~ c1*TSO_A
# TSO_P_SOO_A ~~ c1*TSO_P
# TSO_A_SOO_P ~~ c2*a2pSOO_P
# TSO_P_SOO_A ~~ c2*a2pSOO_A
# TSO_A ~~ c3*a2pSOO_P
# TSO_P ~~ c3*a2pSOO_A
# TSO_A ~~ c4*a2pSOO_A
# TSO_P ~~ c4*a2pSOO_P
# TSO_A_SOO_P ~~ c5*a2pSOO_A
# TSO_P_SOO_A ~~ c5*a2pSOO_P
# TSO_A_SOO_P ~~ c6*TSO_P
# TSO_P_SOO_A ~~ c6*TSO_A
# '
# 
# 
# 
# fit <- sem(model, data=dyad_cswomen)
# ```
# 
# ```{r sem, include=TRUE, results='asis'}
# fit_table <- xtable(parameterEstimates(fit))
# 
# fit_table <- fit_table %>%
#   filter(op=="~") %>%
#   mutate(lhs = ifelse(lhs == "howbody_avg_A", "Actor SSO",
#                       ifelse(lhs=="authenticity_A", "Actor Authenticity",
#                              ifelse(lhs=="howbody_avg_P", "Partner SSO",
#                                     ifelse(lhs=="authenticity_P", "Partner Authenticity",
#                                            ifelse(lhs=="relag_A", "Actor Rel. Agency",
#                                                   ifelse(lhs=="relag_P", "Partner Rel. Agency",
#                                                          ifelse(lhs=="careerasp_A", "Actor Career Aspirations",
#                                                                 ifelse(lhs=="careerasp_P", "Partner Career Aspirations",
#                                                                        ifelse(lhs=="trigram_score_A", "Actor Cog. Performance",
#                                                                               ifelse(lhs=="trigram_score_P", "Partner Cog. Performance", NA)))))))))),
#          rhs = ifelse(rhs=="TSO_A", "Actor TSO",
#                       ifelse(rhs=="a2pSOO_A", "Actor Obj. of Partner",
#                              ifelse(rhs=="a2pSOO_P", "Partner Obj. of Actor",
#                                     ifelse(rhs=="TSO_A_SOO_P", "Actor TSO x Partner Obj.",
#                                            ifelse(rhs == "howbody_avg_A", "Actor SSO",
#                                                   ifelse(rhs=="howbody_avg_P", "Partner SSO",
#                                                          ifelse(rhs=="TSO_P", "Partner TSO",
#                                                                 ifelse(rhs=="TSO_P_SOO_A", "Partner TSO x Actor Obj.",
#                                                                        ifelse(rhs=="authenticity_A", "Actor Authenticity",
#                                                                               ifelse(rhs=="authenticity_P", "Partner Authenticity", NA))))))))))) %>%
#   select(lhs, op, rhs, est, se, z, pvalue) %>%
#   #taking out partner-partner estimates
#   slice(1:5,11:13)
# 
